Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-01-06 paper/tidy-missing-data-paper.Rmd
fix table function ordering

table_of_fun <- tibble::tibble(
  "Missing Function" = c("n_miss", 
                         "prop_miss", 
                         "pct_miss",
                         "pct_miss_var",
                         "pct_miss_case"),
  "missing value" = c(n_miss(airquality),
                      prop_miss(airquality),
                      pct_miss(airquality),
                      pct_miss_case(airquality),
                      pct_miss_var(airquality)),
  "Complete function" = c("n_complete",
                          "prop_complete",
                          "pct_complete",
                          "prop_complete_var",
                          "pct_complete_case"),
  "complete value" = c(n_complete(airquality), 
                       prop_complete(airquality), 
                       pct_complete(airquality),
                       prop_complete_case(airquality), 
                       pct_complete_var(airquality))
) %>%
  mutate_if(is.numeric,round,2)

>>>>

table_of_fun <- tibble::tibble(
  "Missing Function" = c("n_miss", 
                         "prop_miss", 
                         "pct_miss",
                         "pct_miss_case",
                         "pct_miss_var"),
  "missing value" = c(n_miss(airquality),
                      prop_miss(airquality),
                      pct_miss(airquality),
                      pct_miss_case(airquality),
                      pct_miss_var(airquality)),
  "Complete function" = c("n_complete",
                          "prop_complete",
                          "pct_complete",
                          "prop_complete_case",
                          "pct_complete_var"),
  "complete value" = c(n_complete(airquality), 
                       prop_complete(airquality), 
                       pct_complete(airquality),
                       pct_complete_case(airquality), 
                       pct_complete_var(airquality))
) %>%
  mutate_if(is.numeric,round,2)
